\documentclass[11pt]{article}
\usepackage{a4wide,parskip,times}

\begin{document}

\centerline{\Large Title goes here}
\vspace{2em}
\centerline{\Large \emph{An MPhil/PartIII* project/essay* proposal [*delete as appropriate]}}
\vspace{2em}
\centerline{\large A. N. Other (\emph{crsid}), Foo College}
\vspace{1em}
\centerline{\large Project Supervisor: Prof A. B. See}
\vspace{1em}

\begin{abstract}
\textsl{Write an ``elevator pitch''. In other words what's the
  problem, why is it important or interesting, and what's your approach. (100 words)} 
\end{abstract}

\section{Introduction, approach and outcomes (500 words)}

\textsl{Provide an introduction to your project or essay. In particular, try to
  motivate the work and explain the relevant context (general
  background, as well as sufficient detail about any related
  work).}

\textsl{What's the basic idea and approach? What are you thinking of 
doing, and how is it going to solve the problem (or need) you've 
identified. What are you going to ``produce''? 
A project will typically produce one (or perhaps more) of the following:
a piece of software, an evaluation of a published result, a proof, or
the design (and perhaps the construction of) a new piece of hardware. An
essay will typically either review and critique a particular area of the
academic literature, or evaluate a published result or proof. Try to 
name the specific things (and describe them) in this part of the 
proposal -- this will allow you to refer to them in the next.} 

\section{Workplan (500 words)}
\textsl{Project students have approximately 28 weeks between the submission of 
the proposal, and the submission of the dissertation. Essay students have 
approximately 14 weeks.  This section
should account for what you intend to do during that time. One
approach would be to divide the time into two-week chunks, and 
describe the work to be done (and, as relevant, milestones to be 
achieved) in each chunk. You should leave one chunk for writing an essay or two 
chunks for writing a project dissertation. You should leave 1 chunk for contingencies.} 

\newpage
\appendix

\end{document}
